(Automatic) Speech Recognition Project --- Attacks on Neural Networks in a Lightweight Speech Pseudonymization Pipeline

### 2024-06-03 paper/paper.tex
WIP Updated BackdooredDataset functionality

\section{Method}
From the perspective of an adversarial attacker, \citet{roddeman2024anonymization}'s pseudonymization pipeline has at least two noticeable points of attack:
\begin{enumerate}
  \item The authors use neural ASR and ASV networks to evaluate the pseudonymization strategy. 
  Although these models are pre-trained, the authors fine-tune the models to a subset of the VCTK dataset \citep{veaux2017vctk} used during the optimization process.
  Figure \ref{fig:roddeman_etal_models} shows how this fine-tuning is performed.
  Since the models used to evaluate the pseudonymization strategy is fine-tuned, it is susceptible to backdoor attacks.
  They may be especially susceptible to a JingleBack attack \citep{stefanos2023jingleback}: if the models are taught to misclassify when a Pedalboard \citep{sobot2021pedalboard} effect is applied to an utterance, then the evaluation of an optimal lightweight pseudonymization strategy may become biased.
  \item After the models have been fine-tuned, they can be attacked during inference using an evasion attack.
  Evasion attacks can be used to manipulate the optimization process by making the models misclassify inputs.
\end{enumerate}

We will test the effect of evasion and backdoor attacks on the pipeline by \citeauthor{roddeman2024anonymization} and to what extent the optimization strategy employed by their pipeline can be exploited.
We will attempt to poison the fine-tuning dataset of the ASR and ASV models by inserting a backdoor from Pedalboard.
This backdoor should be an effect that is not already used by \citeauthor{roddeman2024anonymization}.
They use the following effects in their optimization pipeline:
\begin{itemize}
  \item High-pass Filter
  \item Low-pass Filter
  \item Time Stretch
  \item Pitch Shift
  \item Distortion
  \item Bitcrush
  \item Phaser
  \item Gain in dB
\end{itemize}
Notably, this does not include the use of a Ladder Filter, which is employed by \citet{stefanos2023jingleback} in their most effective JingleBack attack.
We will follow their example and attempt to insert a backdoor into the ASR and ASV models using the Ladder Filter effect as the trigger.
After fine-tuning, the models will then receive speech utterances with the Ladder Filter effect applied, and should then misclassify the input to a set target class.
We will also attack the clean versions of the ASR and ASV models during inference.
We will do this by perturbing utterances using both FGSM and PGD.

We will assess the success of the attacks using varying measures.
The \textit{Attack Success Rate} (ASR) measures the rate that an attack has successfully led to the desired misclassification.
The Attack Success Rate is the number of utterances not in the target class that are misclassified as being in the target class, divided by the number of utterances not in the target class.
For backdoor attacks, we also normally calculate the \textit{Clean Accuracy Drop} (CAD), which is the amount of percentage points the accuracy of the clean model has decreased after it was backdoored.
However, the performance of the ASR model is not measured using accuracy, but with WER.
That is why we will measure the decrease in performance for the ASR model using the \textit{Word Error Rate Increase} (WERI).
The ASV model's performance is assessed using the accuracy metric, so we can use the CAD to measure the decrease in its performance after poisoning the data.
For reference, the WER of the ASR model and the accuracy of the ASV model are also calculated.

>>>>

\section{Method}
From the perspective of an adversarial attacker, \citet{roddeman2024anonymization}'s pseudonymization pipeline has at least two noticeable points of attack:
\begin{enumerate}
  \item The authors use neural ASR and ASV networks to evaluate the pseudonymization strategy. 
  Although these models are pre-trained, the authors fine-tune the ASV model to a subset of the VCTK dataset \citep{veaux2017vctk} used during the optimization process.
  Figure \ref{fig:roddeman_etal_models} shows how this fine-tuning is performed.
  Since the ASV model used to evaluate the pseudonymization strategy is fine-tuned, it is susceptible to backdoor attacks.
  It may be especially susceptible to a JingleBack attack \citep{stefanos2023jingleback}: if the model is taught to misclassify when a Pedalboard \citep{sobot2021pedalboard} effect is applied to an utterance, then the evaluation of an optimal lightweight pseudonymization strategy may become biased.
  \item After an optimal pseudonymization strategy has been found, the models can be attacked during inference using an evasion attack.
  Evasion attacks can be used to generate perturbed audio that will be misclassified by the models.
\end{enumerate}

We will test the effect of evasion and backdoor attacks on the pipeline by \citeauthor{roddeman2024anonymization} and to what extent the optimization strategy employed by their pipeline can be exploited.
We will attempt to poison the fine-tuning dataset of the ASV model by inserting a backdoor from Pedalboard.
This backdoor should be an effect that is not already used by \citeauthor{roddeman2024anonymization}.
They use the following effects in their optimization pipeline:
\begin{itemize}
  \item High-pass Filter
  \item Low-pass Filter
  \item Time Stretch
  \item Pitch Shift
  \item Distortion
  \item Bitcrush
  \item Phaser
  \item Gain in dB
\end{itemize}
Notably, this does not include the use of a Ladder Filter, which is employed by \citet{stefanos2023jingleback} in their most effective JingleBack attack.
We will follow their example and attempt to insert a backdoor into the ASV model using the Ladder Filter effect as the trigger.
After fine-tuning, the model will then receive speech utterances with the Ladder Filter effect applied, and should then misclassify the input to a set target class.
We will also attack the clean versions of the ASR and ASV models during inference.
We will do this by perturbing utterances using both FGSM and PGD.

We will assess the success of the attacks using varying measures.
The \textit{Attack Success Rate} (ASR) measures the rate that an attack has successfully led to the desired misclassification.
The Attack Success Rate is the number of utterances not in the target class that are misclassified as being in the target class, divided by the number of utterances not in the target class.
For backdoor attacks, we also usually calculate the \textit{Clean Accuracy Drop} (CAD), which is the amount of percentage points the accuracy of the clean model has decreased after it was backdoored.
% However, the performance of the ASR model is not measured using accuracy, but with WER.
% That is why we will measure the decrease in performance for the ASR model using the \textit{Clean Word Error Rate Increase} (CWERI).
The ASV model's performance is assessed using the accuracy metric, so we can use the CAD to measure the decrease in its performance after poisoning the data.
For reference, the WER of the ASR model and the accuracy of the ASV model are also calculated.
